Data dictionary - tidy_dataset
===============================
-------   

**subject**   
Datatype   :  integer (1 - 30)    
An identifier of the subject who carried out the experiment. Identifiers are as below:-      
```{r echo=F, results='markup'}
tidy_dataset <- read.table(file="./tidy_dataset.txt", as.is=T, header=T, sep=" ")
unique(tidy_dataset$subject)
```
          
**activity**     
    Datatype : character   
    An activity in which the the subject was involved in and mesurements were recorded.  
    
```{r echo=F, results='markup'}
require(knitr)

activity_labels <- read.table(file="./UCI HAR Dataset/activity_labels.txt", as.is=T)
names(activity_labels) <- c("code", "activity_description")
activity_labels
```



**Other**  
   Datatype : double:-      
* Time domain signals are prefix ***'t'*** to denote time.   
* Frequency domain signals are prefixed with ***'f'*** to denote frequency.   
* Time body linear acceleration and angular velocity derived from Jerk signals are coded as (tBodyAccJerk_XYZ and tBodyGyroJerk_XYZ).   
* The magnitude of three-dimensional signals were calculated using the Euclidean norm and coded as:-   
  (tBodyAccMag, tGravityAccMag, tBodyAccJerkMag, tBodyGyroMag, tBodyGyroJerkMag). 

These three parameters reflect in the variable names as below:-

```{r echo=F, results='markup'}
tidy_dataset <- read.table(file="./tidy_dataset.txt", as.is=T, header=T, sep=" ")
names(tidy_dataset[3:length(tidy_dataset)])
names(df)
```   


